Making decisions from samples with variable time costs

### 2014-12-19 jhamrick-cs281a.tex
More work on introduction

@@

% talk about SPRT
\cite{wald1947sequential}
\cite{Bitzer:2014ea}
\cite{Gold:2007fo}
\cite{Ratcliff:2008ux}

% Summary
In this paper, we ask the question: how many samples should sample-based agents take before coming to a decision, if the time cost of these samples is unknown? We find the counterintuitive result that the uncertainty in time cost largely doesn't matter; it is nearly optimal for the agent to act using a fixed time cost set to the expected value of the time cost. To show this, we first summarize the formal model as described by \citeA{Vul:2014ba}. Then, we extend this model to handle the case where samples take a variable amount of time. Finally, we apply this model to a behavioral case study.

>>>>

% SPRT
\citeA{Vul:2014ba} examined not just the case where an agent can take a fixed number of samples, but also several policies for taking a variable number of samples depending on how useful the samples are. For example, consider the case where an agent must decide between two options. If they draw samples favoring one of the options with probability 0.95, then the agent can be fairly confident about which is the better option after only a few samples. In contrast, if the probability is 0.55, then the agent would need many samples to be confident about which option is better. Of course, the agent doesn't know what the probability is: that is the point of sampling. One strategy which addresses this issue is known as the \emph{sequential probability ratio test} \cite{wald1947sequential}, or SPRT, and has been used extensively to model a variety of decision making tasks in humans \cite<e.g.>{Gold:2007fo,Ratcliff:2008ux,Bitzer:2014ea}. An agent using SPRT accumulates evidence for one option versus another, and stops sampling once a particular threshold of evidence has been reached. So, rather than optimizing for a fixed number of samples, the agent should optimize for the threshold.

@@

% Summary
In this paper, we ask the question: what SPRT threshold should sample-based agents use when making decisions, if the time cost of taking samples is unknown? We find the counterintuitive result that the uncertainty in time cost largely doesn't matter; it is nearly optimal for the agent to act using a fixed time cost set to the expected value of the time cost. To show this, we first summarize the formal model as described by \citeA{Vul:2014ba}. Then, we extend this model to handle the case where samples take a variable amount of time. Finally, we apply the SPRT model to a behavioral case study in order to understand how people treat variable-time samples.
